The future age structure of scientific disciplines

### 2025-04-15 age_structure_forecasts.qmd
Removed appendix

---
title: "The future age structure of scientific disciplines"
author:
- name: Rob J Hyndman
  affiliations:
    - name: Monash University
      department: Department of Econometrics & Business Statistics
      city: Clayton
      country: Australia
      postal-code: 3800
  email: Rob.Hyndman@monash.edu
  corresponding: true
- name: Kelly Vanh Nguyen
  affiliations:
    - name: Monash University
      department: Department of Econometrics & Business Statistics
      city: Clayton VIC
      country: Australia
      postal-code: 3800
abstract: |
  A brief summary of our ideas
keywords: [blah, blah]
bibliography: refs.bib
wpnumber: no/yr
jelcodes: C10,C14,C22
blind: false
cover: true
linestretch: 1.5
format:
  wp-pdf:
    keep-tex: true
filters:
  - blindable-div
execute:
  eval: false
---

@@

\newpage

# Appendix

```{r}
#| label: tbl-disciplines-stats
#| eval: false
#| tbl-cap: Summary statistics for the scientific disciplines, including the 10th and 90th percentile ages, weighted average age, and weighted median age, calculated from the Australian Census data for the years 2006, 2011, 2016, and 2021.

calculate_statistics <- function(discipline_data, discipline_name, years) {
  stats <- discipline_data |>
    as_tibble() |>
    filter(Year %in% years) |>
    mutate(Age = as.numeric(as.character(Age))) |>
    group_by(Year) |>
    summarise(
      `10th Percentile` = weighted_percentile(Age, Working, prob = 0.1),
      `90th Percentile` = weighted_percentile(Age, Working, prob = 0.9),
      `Weighted Average` = round(sum(Age * Working, na.rm = TRUE) / sum(Working, na.rm = TRUE), 1),
      `Weighted Median` = weighted_percentile(Age, Working, prob = 0.5)
    )

  stats <- stats |> mutate(Discipline = discipline_name)

  return(stats)
}

statistics_math <- calculate_statistics(mathematical_sciences, "Mathematical Sciences", years)
statistics_chem <- calculate_statistics(chemical_sciences, "Chemical Sciences", years)
statistics_earth <- calculate_statistics(earth_sciences, "Earth Sciences", years)
statistics_bio <- calculate_statistics(biological_sciences, "Biological Sciences", years)
statistics_other <- calculate_statistics(other_natural_and_physical_sciences, "Other Natural and Physical Sciences", years)
statistics_nfd <- calculate_statistics(natural_and_physical_sciences__nfd, "Natural and Physical Sciences (n.f.d.)", years)

all_statistics <- bind_rows(statistics_math, statistics_chem, statistics_earth, statistics_bio, statistics_other, statistics_nfd)

kable(all_statistics[, c("Year", "10th Percentile", "90th Percentile", "Weighted Average", "Weighted Median")]) |>
  add_header_above(c("Summary Statistics of Scientific Disciplines" = ncol(all_statistics)), bold = TRUE) |>
  kable_styling(full_width = FALSE) |>
  column_spec(1, width = "10em") |>
  column_spec(2, width = "5em") |>
  column_spec(3, width = "5em") |>
  column_spec(4, width = "5em") |>
  column_spec(5, width = "5em") |>
  column_spec(6, width = "5em") |>
  group_rows("Mathematical Sciences", 1, 4) |>
  group_rows("Chemical Sciences", 5, 8) |>
  group_rows("Earth Sciences", 9, 12) |>
  group_rows("Biological Sciences", 13, 16) |>
  group_rows("Other Natural and Physical Sciences", 17, 20) |>
  group_rows("Natural and Physical Sciences (n.f.d.)", 21, 24)
```

## Mathematical Sciences

```{r}
#| label: fig-mathematicians
#| eval: false
#| fig-cap: Interpolated number of scientists in Mathematical Sciences active in the Australian labour market, 2006–2021, using linear cohort interpolation
#| fig-height: 3.5
#| fig-width: 5.5
mathematical_sciences |>
  autoplot(Working) +
  labs(y = "Number of active scientists") +
  labs(
    title = "Interpolated Working Population",
    subtitle = "Mathematical Sciences\n2006 - 2021"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-future-grads-math
#| eval: false
#| fig-cap: Projected number of Mathematical Sciences graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023.
#| fig-height: 3.5
#| fig-width: 5.5
math_grads <- future_course_leavers_science |>
  filter(discipline == "Mathematical Sciences") |>
  summarise(
    mean = mean(Graduates),
    lo = quantile(Graduates, prob = 0.05),
    hi = quantile(Graduates, prob = 0.95)
  )
ggplot(math_grads) +
    aes(x = Year) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
    geom_line(aes(y = mean), color = "#c14b14") +
    geom_line(data = course_leavers_lvl4 |> filter(discipline == "Mathematical Sciences"), aes(y = Graduates)) +
  labs(y = "Number of graduates",
    title = "Forecast of Graduates",
    subtitle = "Mathematical Sciences\nForecasted Years: 2024 - 2041"
  ) +
 scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-net-migrants-maths
#| eval: false
#| fig-cap: Net migration of scientists in Mathematical Sciences by age, 2006–2020.
#| fig-height: 3.5
#| fig-width: 5.5

mathematical_sciences |>
  autoplot(Migrants) +
  scale_x_continuous(breaks = seq(10,100,by=10)) +
  labs(
    y = "Number of net migrants",
    title = "Estimated Net Migration",
    subtitle = "Mathematical Sciences\n2006 - 2020"
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha=0.5) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-future-mathematicians-2035
#| eval: false
#| fig-cap: Forecasted age distribution of the working population for Mathematical Sciences in 2025 and 2035, comparing changes over 10 years. Shaded areas represent 90% prediction intervals.
#| fig-height: 3.5
#| fig-width: 5.5
# 2025 and 2035
eg_forecast <- future_mathematical_sciences |>
  filter(Year %in% c(2025, 2035)) |>
  group_by(Age) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )

# Overlay
ggplot(eg_forecast) +
    aes(x = Age, color = factor(Year)) +
    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
    geom_line(aes(y = mean), size = 0.6) +
  labs(y = "Number of working scientists",
    title = "Forecast of Working Population",
    subtitle = "Mathematical Sciences",
      color = "Forecast Year",
      fill = "Forecast Year"
    ) +
    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
    theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7),
    legend.position = "top"
  )
```

```{r}
#| label: fig-total-future-mathematicians
#| eval: false
#| fig-cap: Forecasted total number of working scientists for Mathematical Sciences (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.
#| fig-height: 3.5
#| fig-width: 5.5

sum_mathematical_sciences  <- mathematical_sciences |>
  as_tibble() |>
  group_by(Year) |>
  summarise(Working = sum(Working), .groups = "drop")
sum_future_mathematical_sciences <- future_mathematical_sciences |>
  as_tibble() |>
  group_by(Year, .rep) |>
  summarise(Working = sum(Working), .groups = "drop")  |>
  group_by(Year) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )
ggplot(sum_future_mathematical_sciences) +
    aes(x = Year) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
    geom_line(aes(y = mean), color = "#c14b14") +
    geom_line(data = sum_mathematical_sciences, aes(y = Working)) +
 labs(y = "Total number of working scientists") +
  labs(
    title = "Forecast of Total Working Population",
    subtitle = "Mathematical Sciences\nForecasted Years: 2022 - 2041"
  ) +
  scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
  scale_y_continuous(labels = scales::comma_format()) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

## Chemical Sciences

```{r}
#| label: fig-chemists
#| eval: false
#| fig-cap: Interpolated number of scientists in Chemical Sciences active in the Australian labour market, 2006–2021, using linear cohort interpolation
#| fig-height: 3.5
#| fig-width: 5.5

chemical_sciences |>
  autoplot(Working) +
  labs(y = "Number of active scientists") +
  labs(
    title = "Interpolated Working Population",
    subtitle = "Chemical Sciences\n2006 - 2021"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-future-grads-chem
#| eval: false
#| fig-cap: Projected number of Chemical Sciences graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023.
#| fig-height: 3.5
#| fig-width: 5.5

chem_grads <- future_course_leavers_science |>
  filter(discipline == "Chemical Sciences") |>
  summarise(
    mean = mean(Graduates),
    lo = quantile(Graduates, prob = 0.05),
    hi = quantile(Graduates, prob = 0.95)
  )
ggplot(chem_grads) +
    aes(x = Year) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
    geom_line(aes(y = mean), color = "#c14b14") +
    geom_line(data = course_leavers_lvl4 |> filter(discipline == "Chemical Sciences"), aes(y = Graduates)) +
  labs(y = "Number of graduates",
    title = "Forecast of Graduates",
    subtitle = "Chemical Sciences\nForecasted Years: 2024 - 2041"
  ) +
 scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-net-migrants-chem
#| eval: false
#| fig-cap: Net migration of scientists in Chemical Sciences by age, 2006–2020.
#| fig-height: 3.5
#| fig-width: 5.5

chemical_sciences |>
  autoplot(Migrants) +
  scale_x_continuous(breaks = seq(10,100,by=10)) +
  labs(
    y = "Number of net migrants",
    title = "Estimated Net Migration",
    subtitle = "Chemical Sciences\n2006 - 2020"
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha=0.5) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-future-chemists-2035
#| eval: false
#| fig-cap: Forecasted age distribution of the working population for Chemical Sciences in 2025 and 2035, comparing changes over 10 years. Shaded areas represent 90% prediction intervals.
#| fig-height: 3.5
#| fig-width: 5.5

# 2025 and 2035
eg_forecast <- future_chemical_sciences |>
  filter(Year %in% c(2025, 2035)) |>
  group_by(Age) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )

# Overlay
ggplot(eg_forecast) +
    aes(x = Age, color = factor(Year)) +
    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
    geom_line(aes(y = mean), size = 0.6) +
  labs(y = "Number of working scientists",
    title = "Forecast of Working Population",
    subtitle = "Chemical Sciences",
      color = "Forecast Year",
      fill = "Forecast Year"
    ) +
    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7),
    legend.position = "top"
  )
```

```{r}
#| label: fig-total-future-chemists
#| eval: false
#| fig-cap: Forecasted total number of working scientists for Chemical Sciences (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.
#| fig-height: 3.5
#| fig-width: 5.5

sum_chemical_sciences  <- chemical_sciences |>
  as_tibble() |>
  group_by(Year) |>
  summarise(Working = sum(Working), .groups = "drop")
sum_future_chemical_sciences <- future_chemical_sciences |>
  as_tibble() |>
  group_by(Year, .rep) |>
  summarise(Working = sum(Working), .groups = "drop")  |>
  group_by(Year) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )
ggplot(sum_future_chemical_sciences) +
    aes(x = Year) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
    geom_line(aes(y = mean), color = "#c14b14") +
    geom_line(data = sum_chemical_sciences, aes(y = Working)) +
 labs(y = "Total number of working scientists") +
  labs(
    title = "Forecast of Total Working Population",
    subtitle = "Chemical Sciences\nForecasted Years: 2022 - 2041"
  ) +
  scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
  scale_y_continuous(labels = scales::comma_format()) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

## Earth Sciences

```{r}
#| label: fig-earthscientists
#| eval: false
#| fig-cap: Interpolated number of scientists in Earth Sciences active in the Australian labour market, 2006–2021, using linear cohort interpolation
#| fig-height: 3.5
#| fig-width: 5.5

earth_sciences |>
  autoplot(Working) +
  labs(
    y = "Number of active scientists",
    title = "Interpolated Working Population",
    subtitle = "Earth Sciences\n2006 - 2021"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-future-grads-earth
#| eval: false
#| fig-cap: Projected number of Earth Sciences graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023.
#| fig-height: 3.5
#| fig-width: 5.5

earth_grads <- future_course_leavers_science |>
  filter(discipline == "Earth Sciences") |>
  summarise(
    mean = mean(Graduates),
    lo = quantile(Graduates, prob = 0.05),
    hi = quantile(Graduates, prob = 0.95)
  )
ggplot(earth_grads) +
    aes(x = Year) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
    geom_line(aes(y = mean), color = "#c14b14") +
    geom_line(data = course_leavers_lvl4 |> filter(discipline == "Earth Sciences"), aes(y = Graduates)) +
  labs(y = "Number of graduates",
    title = "Forecast of Graduates",
    subtitle = "Earth Sciences\nForecasted Years: 2024 - 2041"
  ) +
 scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-net-migrants-earth
#| eval: false
#| fig-cap: Net migration of scientists in Earth Sciences by age, 2006–2020.
#| fig-height: 3.5
#| fig-width: 5.5

earth_sciences |>
  autoplot(Migrants) +
  scale_x_continuous(breaks = seq(10,100,by=10)) +
  labs(
    y = "Number of net migrants",
    title = "Estimated Net Migration",
    subtitle = "Earth Sciences\n2006 - 2020"
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha=0.5) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-future-earthscientists-2035
#| eval: false
#| fig-cap: Forecasted age distribution of the working population for Earth Sciences in 2025 and 2035, comparing changes over 10 years. Shaded areas represent 90% prediction intervals.
#| fig-height: 3.5
#| fig-width: 5.5

# 2025 and 2035
eg_forecast <- future_earth_sciences |>
  filter(Year %in% c(2025, 2035)) |>
  group_by(Age) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )

# Overlay
ggplot(eg_forecast) +
    aes(x = Age, color = factor(Year)) +
    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
    geom_line(aes(y = mean), size = 0.6) +
  labs(y = "Number of working scientists",
    title = "Forecast of Working Population",
    subtitle = "Earth Sciences",
      color = "Forecast Year",
      fill = "Forecast Year"
    ) +
    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
    theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7),
    legend.position = "top"
  )
```

```{r}
#| label: fig-total-future-earthscientists
#| eval: false
#| fig-cap: Forecasted total number of working scientists for Earth Sciences (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.
#| fig-height: 3.5
#| fig-width: 5.5

sum_earth_sciences  <- earth_sciences |>
  as_tibble() |>
  group_by(Year) |>
  summarise(Working = sum(Working), .groups = "drop")
sum_future_earth_sciences <- future_earth_sciences |>
  as_tibble() |>
  group_by(Year, .rep) |>
  summarise(Working = sum(Working), .groups = "drop")  |>
  group_by(Year) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )
ggplot(sum_future_earth_sciences) +
    aes(x = Year) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
    geom_line(aes(y = mean), color = "#c14b14") +
    geom_line(data = sum_earth_sciences, aes(y = Working)) +
 labs(y = "Total number of working scientists") +
  labs(
    title = "Forecast of Total Working Population",
    subtitle = "Earth Sciences\nForecasted Years: 2022 - 2041"
  ) +
  scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
  scale_y_continuous(labels = scales::comma_format()) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

## Biological Sciences

```{r}
#| label: fig-biologists
#| eval: false
#| fig-cap: Interpolated number of scientists in Biological Sciences active in the Australian labour market, 2006–2021, using linear cohort interpolation
#| fig-height: 3.5
#| fig-width: 5.5

biological_sciences |>
  autoplot(Working) +
  labs(y = "Number of active scientists") +
  labs(
    title = "Interpolated Working Population",
    subtitle = "Biological Sciences\n2006 - 2021"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-future-grads-bio
#| eval: false
#| fig-cap: Projected number of Biological Sciences graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023. intervals.
#| fig-height: 3.5
#| fig-width: 5.5

bio_grads <- future_course_leavers_science |>
  filter(discipline == "Biological Sciences") |>
  summarise(
    mean = mean(Graduates),
    lo = quantile(Graduates, prob = 0.05),
    hi = quantile(Graduates, prob = 0.95)
  )
ggplot(bio_grads) +
    aes(x = Year) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
    geom_line(aes(y = mean), color = "#c14b14") +
    geom_line(data = course_leavers_lvl4 |> filter(discipline == "Biological Sciences"), aes(y = Graduates)) +
  labs(y = "Number of graduates",
    title = "Forecast of Graduates",
    subtitle = "Biological Sciences\nForecasted Years: 2024 - 2041"
  ) +
 scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-net-migrants-biology
#| eval: false
#| fig-cap: Net migration of scientists in Biological Sciences by age, 2006–2020.
#| fig-height: 3.5
#| fig-width: 5.5

biological_sciences |>
  autoplot(Migrants) +
  scale_x_continuous(breaks = seq(10,100,by=10)) +
  labs(
    y = "Number of net migrants",
    title = "Estimated Net Migration",
    subtitle = "Biological Sciences\n2006 - 2020"
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha=0.5) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-future-biologists-2035
#| eval: false
#| fig-cap: Forecasted age distribution of the working population for Biological Sciences in 2025 and 2035, comparing changes over 10 years. Shaded areas represent 90% prediction intervals.
#| fig-height: 3.5
#| fig-width: 5.5

# 2025 and 2035
eg_forecast <- future_biological_sciences |>
  filter(Year %in% c(2025, 2035)) |>
  group_by(Age) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )

# Overlay
ggplot(eg_forecast) +
    aes(x = Age, color = factor(Year)) +
    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
    geom_line(aes(y = mean), size = 0.6) +
  labs(y = "Number of working scientists",
    title = "Forecast of Working Population",
    subtitle = "Biological Sciences",
      color = "Forecast Year",
      fill = "Forecast Year"
    ) +
    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
    theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7),
    legend.position = "top"
  )
```

```{r}
#| label: fig-total-future-biologists
#| eval: false
#| fig-cap: Forecasted total number of working scientists for Biological Sciences (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.
#| fig-height: 3.5
#| fig-width: 5.5

sum_biological_sciences  <- biological_sciences |>
  as_tibble() |>
  group_by(Year) |>
  summarise(Working = sum(Working), .groups = "drop")
sum_future_biological_sciences <- future_biological_sciences |>
  as_tibble() |>
  group_by(Year, .rep) |>
  summarise(Working = sum(Working), .groups = "drop")  |>
  group_by(Year) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )
ggplot(sum_future_biological_sciences) +
    aes(x = Year) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
    geom_line(aes(y = mean), color = "#c14b14") +
    geom_line(data = sum_biological_sciences, aes(y = Working)) +
 labs(y = "Total number of working scientists") +
  labs(
    title = "Forecast of Total Working Population",
    subtitle = "Biological Sciences\nForecasted Years: 2022 - 2041"
  ) +
  scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
  scale_y_continuous(labels = scales::comma_format()) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

## Other Natural and Physical Sciences

```{r}
#| label: fig-otherscientists
#| eval: false
#| fig-cap: Interpolated number of scientists in Other Natural and Physical Sciences active in the Australian labour market, 2006–2021, using linear cohort interpolation
#| fig-height: 3.5
#| fig-width: 5.5

other_natural_and_physical_sciences |>
  autoplot(Working) +
  labs(y = "Number of active scientists") +
  labs(
    title = "Interpolated Working Population",
    subtitle = "Other Natural and Physical Sciences\n2006 - 2021"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-future-grads-other
#| eval: false
#| fig-cap: Projected number of Other Natural and Physical Sciences graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023.
#| fig-height: 3.5
#| fig-width: 5.5

other_grads <- future_course_leavers_science |>
  filter(discipline == "Other Natural and Physical Sciences") |>
  summarise(
    mean = mean(Graduates),
    lo = quantile(Graduates, prob = 0.05),
    hi = quantile(Graduates, prob = 0.95)
  )
ggplot(other_grads) +
    aes(x = Year) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
    geom_line(aes(y = mean), color = "#c14b14") +
    geom_line(data = course_leavers_lvl4 |> filter(discipline == "Other Natural and Physical Sciences"), aes(y = Graduates)) +
  labs(y = "Number of graduates",
    title = "Forecast of Graduates",
    subtitle = "Other Natural and Physical Sciences\nForecasted Years: 2024 - 2041"
  ) +
 scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-net-migrants-other
#| eval: false
#| fig-cap: Net migration of scientists in Other Natural and Physical Sciences by age, 2006–2020.
#| fig-height: 3.5
#| fig-width: 5.5

other_natural_and_physical_sciences |>
  autoplot(Migrants) +
  scale_x_continuous(breaks = seq(10,100,by=10)) +
  labs(
    y = "Number of net migrants",
    title = "Estimated Net Migration",
    subtitle = "Other Natural and Physical Sciences\n2006 - 2020"
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha=0.5) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-future-otherscientists-2035
#| eval: false
#| fig-cap: Forecasted age distribution of the working population for Other Natural and Physical Sciences in 2025 and 2035, comparing changes over 10 years. Shaded areas represent 90% prediction intervals.
#| fig-height: 3.5
#| fig-width: 5.5

# 2025 and 2035
eg_forecast <- future_other_natural_and_physical_sciences |>
  filter(Year %in% c(2025, 2035)) |>
  group_by(Age) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )

>>>>

---
title: "The future age structure of scientific disciplines"
author:
- name: Rob J Hyndman
  affiliations:
    - name: Monash University
      department: Department of Econometrics & Business Statistics
      city: Clayton
      country: Australia
      postal-code: 3800
  email: Rob.Hyndman@monash.edu
  corresponding: true
- name: Kelly Vanh Nguyen
  affiliations:
    - name: Monash University
      department: Department of Econometrics & Business Statistics
      city: Clayton VIC
      country: Australia
      postal-code: 3800
abstract: |
  A brief summary of our ideas
keywords: [blah, blah]
bibliography: refs.bib
wpnumber: no/yr
jelcodes: C10,C14,C22
blind: false
cover: true
linestretch: 1.5
include-in-header: preamble.tex
format:
  wp-pdf:
    keep-tex: true
filters:
  - blindable-div
execute:
  eval: false
---

@@
